---
title: "R Notebook"
output: Hypothesis
---

Load the library

```{r}
library(readxl)
```


## Hypothesis

p = proportion of low-floor bus

- $H_0$: $p \geq 0.9$
- $H_1$: $p < 0.9$

```{r}
p_low <- .9
```


## Population

1.  中興巴士
2.  光華巴士
3.  新北客運
4.  淡水客運
5.  指南客運
6.  首都客運
7.  臺北客運
8.  大都會客運
9.  三重客運
10. 大有巴士
11. 新店客運
12. 東南客運

監理站無行政院國軍退除役官兵輔導委員會(大南汽車、欣欣客運)及未參加聯營之客運業者(皇家客運)

```{r}
com <- data.frame(name=c("中興巴士","光華巴士","新北客運","淡水客運","指南客運","首都客運","臺北客運","大都會客運","三重客運","大有巴士","新店客運","東南客運", "大南汽車", "欣欣客運"), count=c(365, 328, 83, 199, 538, 866, 981, 961, 977, 118, 304, 110, 246, 414))

print(com)
```

## Sampling

We use stratified sampling to keep each company's proportion of number of buses same as that in population.

Sample size: 54

```{r}
sample_size <- round(com$count/sum(com$count) * 60)
cat("Sample size:", sample_size)
```


Random select the bus by their ordering.

```{r}
set.seed(1001)
getBus <- function(index) {
  return(sample(1:com$count[index], sample_size[index]))
}

sam <- lapply(1:nrow(com), getBus)
names(sam) <- com$name
print(sam)
```

The result collected on our own

```{r}
low <- read_excel("data/low_floor.xlsx")
print(low)
```

Check for np and n(p-1)

```{r}
cat("np =", p_low*54)
cat("n(1-p) =", (1-p_low)*54)
```

Since both of np and n(1-p) are larger than 5, we can approximate the distribution of population with normal distribution.

Compute the p-value

```{r}
p_sample <- sum(low$`Is Low Floor`)/nrow(low)
sd_low <- sqrt(.9*(1-.9)/sum(com$count))
print(sd_low)
```

```{r}
.9+sqrt(.9*(1-.9)/60)*qnorm(.01, lower.tail = TRUE)
```

```{r}
.8+sqrt(.8*(1-.8)/60)*qnorm(.01, lower.tail = TRUE)
```

```{r}
.86+sqrt(.86*(1-.86)/60)*qnorm(.01/2, lower.tail = TRUE)
```

