---
title: "Statistic 2019 a Final Project (Group 2)"
output: html_notebook
---

# Setting up

Close the warning

```{r}
options(warn=-1)
```


Load the library.

```{r}
library(readxl)    # read_excel
library(moments)   # skewness, kurtosis
```

Set the `modal` function to compute modal class

```{r}
Mode <- function(x) {
  t <- table(x)
  return(names(t)[t==max(t)])
}
```

Set the `Range` function to compute range

```{r}
Range <- function(x) {
  return(max(x)-min(x))
}
```

Set the `pvar` function to compute variance of population

```{r}
pvar <- function(x) {
  n <- length(x)
  return(var(x) * (n-1) / n)
}
```

Set the `psd` function to compute the standard deviation of population

```{r}
psd <- function(x) {
  return(sqrt(pvar(x)))
}
```

Set the `pcv` function to compute coefficient of variation of population

```{r}
pcv <- function(x) {
  return(psd(x)/mean(x))
}
```

Set the `pDescriptive_S` to compute the descriptive statistic of population

```{r}
pDescriptive_S <- function(x) {
   library(moments)
   DS_V <- vector("numeric", length = 13)
   DS_V[1] <- mean(x)
   DS_V[2] <- median(x)
   DS_V[3] <- psd(x)
   DS_V[4] <- pvar(x)
   DS_V[5] <- skewness(x)
   DS_V[6] <- kurtosis(x)
   DS_V[8] <- min(x)
   DS_V[9] <- max(x)
   DS_V[10] <- sum(x)
   DS_V[11] <- length(x)
   DS_V[7] <- max(x) - min(x)
   DS_V[12] <- psd(x) / sqrt(length(x))
   DS_V[13] <- pcv(x)
   names(DS_V) <- c("mean", "median", "stdev", "variance", "skewness", "kurtosis", "range", "min", "max", "sum", "size", "std err", "coef of variation")
   return(DS_V)
}
```

# Bus Efficiency

Read the excel file.

```{r}
bus_efficiency <- read_excel("Stat_2019_a_2_bus-efficiency.xlsx", na=c("-","..."))
print(head(bus_efficiency))
```

Fill the recording year to each row, reassign the column names and remove the bus line that was not recorded.

```{r}
years <- bus_efficiency$...1[!is.na(bus_efficiency$...1)]
cnt <- 1
for (y in years) {
  y <- substr(y, 1, nchar(y)-1)
  bus_efficiency$...1[cnt] <- y
  cnt = cnt + 1
  while(cnt <= length(bus_efficiency$...1) && is.na(bus_efficiency$...1[cnt])) {
    bus_efficiency$...1[cnt] <- y
    cnt = cnt + 1
  }
}
colnames(bus_efficiency) <- c("Year", "Name", "Times", "Length", "Customer", "Average.Customer", "Profit", "Average.Profit")
bus_efficiency <- bus_efficiency[complete.cases(bus_efficiency),]
print(head(bus_efficiency))
```

Apply the descriptive statistic to the bus efficiency in 2018.

```{r}
year <- 107
ds <- data.frame()
for (i in colnames(bus_efficiency)[3:ncol(bus_efficiency)]) {
  ds <- rbind(ds, pDescriptive_S(bus_efficiency[[i]][bus_efficiency$Year == year]))
}
colnames(ds) <- c("mean", "median", "stdev", "variance", "skewness", "kurtosis", "range", "min", "max", "sum", "size", "std err", "coef of variation")
rownames(ds) <- colnames(bus_efficiency)[3:ncol(bus_efficiency)]
ds
```


